### 2025-01-18 Dustbound/English/Dustbound_English_I/paper.tex
chore: :building_construction: 修改了试题的存放位置

\documentclass{exam-zh}

\usepackage{xeCJK}
\usepackage{background}
\usepackage{needspace}
\usepackage{listing}

\examsetup{
  page = {
    foot-content = 「赴尘杯」英语试题第 ; 页（共 ; 页）
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

\title{「赴尘杯」2025 年普通高中学业水平选择性考试适应性演练}
\subject[3.5em]{英语 I}

\begin{document}

\information{
  姓名\underline{\hspace{6em}},
  准考证号\underline{\hspace{15em}},
  座位号\underline{\hspace{6em}}
}

\vspace{1\baselineskip}

\secret

\maketitle

本试卷共 16 页，67 题。全卷满分 150 分。考试用时 120 分钟。

\begin{notice}[][itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt]
\item 答卷前，考生务必将自己的姓名、考生号等填写在答题卡上。
\item 回答选择题时，选出每小题答案后，用铅笔把答题卡上对应题目的答案标号涂黑，如需改动，用橡皮擦干净后，再选涂其他答案标号。回答非选择题时，将答案写在答题卡上，写在本试卷上无效。
\item 考试结束后，将本试卷和答题卡一并交回。
\end{notice}

\warning{持有者应知晓本试题仍处于早期构建中，其排版、内容或分发形式可能会在构建过程中发生较大的变动，恕不另行通知。}

\begin{flushleft}
  {\bfseries 第二部分 \hspace{0.5em} 阅读理解（共两节，满分 50 分）}

{\bfseries 第一节（共 15 小题；每小题 2.5 分，满分 37.5 分)}
\end{flushleft}

阅读下列短文，从每题所给的 A、B、C 和 D 四个选项中，选出最佳答案。

\needspace{4\baselineskip}
{\centering \bfseries A \par}

{\centering \bfseries Unified Extensible Firmware Interface / Secure Boot \par}

Secure Boot is a security feature found in the UEFI standard, designed to add a layer of protection to the pre-boot process: by maintaining a cryptographically (使用密码学方法地) signed list of binaries authorized or forbidden to run at boot, it helps in improving the confidence that the machine core boot components (boot manager, kernel, initramfs) have not been tampered with.

As such it can be seen as a continuation or complement to the efforts in securing one's computing environment, reducing the attack surface that other software security solutions such as system encryption cannot easily cover, while being totally distinct and not dependent on them. Secure Boot just stands on its own as a component of current security practices, with its own set of pros and cons.

\needspace{2\baselineskip}
\textbf{I. Before Booting the OS}

(This content is missing and needs to be completed in Question 3.)

\needspace{2\baselineskip}
\textbf{II. Booting an installation medium}

In order to boot an installation medium in a Secure Boot system, you will need to either disable Secure Boot or modify the image in order to add a signed boot loader.

\begingroup
\leftskip=2em

\needspace{2\baselineskip}
\textbf{i. Disabling Secure Boot}

The Secure Boot feature can be disabled via the UEFI firmware interface. How to access the firmware configuration is described in \underline{Before booting the OS}. Some motherboards (this is the case in a Packard Bell laptop and recent Xiaomi laptops) only allow to disable secure boot if you have set an administrator password that can be removed afterwards. See also \underline{Rod Smith's Disabling Secure Boot}.

\needspace{2\baselineskip}
\textbf{ii. Editing the installation medium}

If you are using a USB flash installation medium, then it is possible to manually edit the EFI system partition on the medium to add support for Secure Boot.

\par
\endgroup

\needspace{2\baselineskip}
\textbf{III. Implementing Secure Boot}

Using a signed boot loader means using a boot loader signed with Microsoft's key. There are two known signed boot loaders: PreLoader and shim. Their purpose is to chainload other EFI binaries (usually boot loaders). Since Microsoft would never sign a boot loader that automatically launches any unsigned binary, PreLoader and shim use an allowlist called Machine Owner Key list, abbreviated MokList. If the SHA256 hash of the binary (Preloader and shim) or key the binary is signed with (shim) is in the MokList they execute it, if not they launch a key management utility which allows enrolling the hash or key.

\begingroup
\leftskip=2em

\needspace{2\baselineskip}
\textbf{i. PreLoader}

When run, PreLoader tries to launch \texttt{loader.efi}. If the hash of \texttt{loader.efi} is not in MokList, PreLoader will launch \texttt{HashTool.efi}. In HashTool you must enroll the hash of the EFI binaries you want to launch, that means your boot loader (\texttt{loader.efi}) and kernel. Each time you update any of the binaries (e.g. boot loader or kernel) you will need to enroll their new hash.

\needspace{2\baselineskip}
\textbf{(1) Set up PreLoader}

\textbf{NOTE:} \texttt{PreLoader.efi} and \texttt{HashTool.efi} in \texttt{efitools} package are not signed, so their usefulness is limited. You can get a signed \texttt{PreLoader.efi} and \texttt{HashTool.efi} from \texttt{preloader-signed}\textsuperscript{AUR} or download them manually.

Install \texttt{preloader-signed}\textsuperscript{AUR} and copy \texttt{PreLoader.efi} and \texttt{HashTool.efi} to the boot loader directory, then copy over the boot loader binary and rename it to \texttt{loader.efi}. Finally, create a new NVRAM entry to boot \texttt{PreLoader.efi}. After these steps, this entry should be added to the list as the first to boot; check with the \texttt{efibootmgr} command and adjust the boot-order if necessary.

\needspace{2\baselineskip}
\textbf{(2) Fallback}

If there are problems booting the custom NVRAM entry, copy \texttt{HashTool.efi} and \allowbreak \texttt{loader.efi} to the default loader location booted automatically by UEFI systems. Copy over \texttt{PreLoader.efi} and rename it.

For particularly intransigent UEFI implementations, copy \texttt{PreLoader.efi} to the default loader location used by Windows systems. Then as before, copy \texttt{HashTool.efi} and \texttt{loader.efi} to \texttt{esp/EFI/Microsoft/Boot/}.

If dual-booting with Windows, backup the original \texttt{bootmgfw.efi} first as replacing it may cause problems with Windows updates. When the system starts with Secure Boot enabled, follow the steps above to enroll \texttt{loader.efi} and \texttt{/vmlinuz-linux} (or whichever kernel image is being used).

\needspace{2\baselineskip}
\textbf{(3) How to use while booting?}

A message will show up that says \textit{Failed to Start loader... I will now execute HashTool.} To use HashTool for enrolling the hash of \texttt{loader.efi} and \texttt{vmlinuz.efi}, follow these steps. These steps assume titles for a remastered archiso installation media. The exact titles you will get depend on your boot loader setup.

\begin{itemize}
\item Select \textit{OK}.

\item In the HashTool main menu, select \textit{Enroll Hash}, choose \texttt{\\loader.efi} and confirm with \textit{Yes}. Again, select \textit{Enroll Hash} and \texttt{archiso} to enter the archiso directory, then select \texttt{vmlinuz.efi} and confirm with \textit{Yes}. Then choose \textit{Exit} to return to the boot device selection menu.

\item In the boot device selection menu choose \textit{Arch Linux archiso x86\_64 UEFI CD}.
\end{itemize}

\needspace{2\baselineskip}
\textbf{ii. shim}

When run, shim tries to launch \texttt{grubx64.efi}. If MokList does not contain the hash of \texttt{grubx64.efi} or the key it is signed with, shim will launch MokManager (\texttt{mmx64.efi}). In MokManager you must enroll the hash of the EFI binaries you want to launch (your boot loader (\texttt{grubx64.efi}) and kernel) or enroll the key they are signed with.

Using hash is simpler, but each time you update your boot loader or kernel you will need to add their hashes in MokManager. With MOK you only need to add the key once, but you will have to sign the boot loader and kernel each time it updates.

\par
\endgroup

\needspace{2\baselineskip}
\textbf{IV. Protecting Secure Boot}

The only way to prevent anyone with physical access from disabling Secure Boot is to protect the firmware settings with a password. Most UEFI firmwares provide such a feature, usually listed under the "Security" section in the firmware settings.

\needspace{4\baselineskip}
\begin{question}
Which of the following statements about Secure Boot is INCORRECT?
\begin{choices}
\item Secure Boot represents a critical security mechanism embedded within the UEFI standard.

\item Secure Boot functions by enforcing a policy that restricts the execution of boot-time binaries to those that are cryptographically signed and thereby verified as authentic.

\item Secure Boot ensures the integrity of core boot components and the efficacy of system encryption relies on the presence or state of Secure Boot.

\item Secure Boot operates independently of other security measures and provides an additional layer of defense against pre-boot attacks.
\end{choices}
\end{question}

\needspace{4\baselineskip}
\begin{question}
Which of the following statements about the possible usage and configuration of Secure Boot is CORRECT?

\begin{choices}
\item Recent iterations of Xiaomi laptops give users access to the configuration of Secure Boot within the firmware only if the administrator password remains active after setting up. Users can possibly set the password in the "Security" section in the firmware settings.

\item Developers of Linux distributions have the capability to assist users to employ PreLoader which includes HashTool, a mechanism which facilitates the integration of the keys utilized for digitally signing EFI binary files into the Machine Owner Key List (MokList) of the user's laptop.

\item When configuring Secure Boot using PreLoader and encountering issues with booting a custom NVRAM entry, it is always necessary to copy \texttt{HashTool.efi} and \texttt{loader.efi} to the UEFI system's default automatic boot loader location. Subsequently, \texttt{PreLoader.efi} must be copied to the default boot loader location used by Windows systems.

\item During the boot process, suppose HashTool is used to enroll the hashes of \texttt{loader.efi} and \texttt{vmlinuz.efi}. Start by selecting \textit{OK} to begin. Enroll the hash for \texttt{loader.efi} by choosing \textit{Enroll Hash} and confirming with \textit{Yes}, and then repeat the process for \texttt{vmlinuz.efi}. Finally, exit HashTool to return to the boot device selection menu, and select the appropriate Arch Linux boot option (such as \textit{Arch Linux archiso x86\_64 UEFI CD}), depending on your boot loader configuration, to start the system.
\end{choices}
\end{question}

\needspace{4\baselineskip}
\begin{question}
Which content is possibly included in \underline{Before booting the OS}?

\needspace{3\baselineskip}
A.
\begin{quote}
  At this point, one has to look at the firmware setup. If the machine was booted and is running, in most cases it will have to be rebooted.

  You may access the firmware configuration by pressing a special key during the boot process. The key to use depends on the firmware. It is usually one of Esc, F2, Del or possibly another Fn key. Sometimes the right key is displayed for a short while at the beginning of the boot process. The motherboard manual usually records it. You might want to press the key, and keep pressing it, immediately following powering on the machine, even before the screen actually displays anything.

  After entering the firmware setup, be careful not to change any settings without prior intention. Usually there are navigation instructions, and short help for the settings, at the bottom of each setup screen. The setup itself might be composed of several pages. You will have to navigate to the correct place. The interesting setting might be simply denoted by secure boot, which can be set on or off.
\end{quote}

\needspace{3\baselineskip}
B.
\begin{quote}
  There are certain conditions making for an ideal setup of Secure boot:

  \begin{itemize}
    \item UEFI considered mostly trusted (despite having some well known criticisms and vulnerabilities) and necessarily protected by a strong password.
    \item Default manufacturer/third party keys are not in use, as they have been shown to weaken the security model of Secure Boot by a great margin.
    \item UEFI directly loads a user-signed EFI boot stub-compatible unified kernel image (no boot manager), including microcode (if applicable) and initramfs so as to maintain throughout the boot process the chain of trust established by Secure Boot and reduce the attack surface.
    \item Use of full drive encryption, so that the tools and files involved in the kernel image creation and signing process cannot be accessed and tampered with by someone having physical access to the machine.
    \item Some further improvements may be obtained by using a TPM.
  \end{itemize}

  A simple and fully self-reliant setup is described in \underline{Using your own keys}, while \allowbreak \underline{Using a signed boot loader} makes use of intermediate tools signed by a third-party.
\end{quote}

\needspace{3\baselineskip}
C.
\begin{quote}
  Replacing the platform keys with your own can end up bricking hardware on some machines, including laptops, making it impossible to get into the firmware settings to rectify the situation. This is due to the fact that some device (e.g GPU) firmware (OpROMs), that get executed during boot, are signed using Microsoft 3rd Party UEFI CA certificate or vendor certificates. This is the case in many Lenovo Thinkpad X, P and T series laptops which uses the Lenovo CA certificate to sign UEFI applications and firmware.

  \textbf{DO NOT} copy the \texttt{noPK.auth} file to the EFI system partition (ESP) of your PC! If you do this, and someone e.g. steals your PC, this person can delete the personal Platform Key in the UEFI Secure Boot firmware again, turn on "Setup Mode" on your PC again and replace your Secure Boot Keys (PK, KEK, db, dbx) with their own Platform Key, thereby defeating the whole purpose of UEFI Secure Boot. Only you should be able to replace the Platform Key, so only you should have access to the \texttt{noPK.auth} file. Therefore keep the \texttt{noPK.auth} file in a secret, safe place where only you have access to.
\end{quote}

\needspace{3\baselineskip}
D.
\begin{quote}
  Point the current boot device to the one which has the Arch Linux installation medium. Typically it is achieved by pressing a key during the POST phase, as indicated on the splash screen. Refer to your motherboard's manual for details.

  When the installation medium's boot loader menu appears,

  \begin{itemize}
    \item if you used the ISO, select Arch Linux install medium and press Enter to enter the installation environment.

    \item if you used the Netboot image, choose a geographically close mirror from Mirror menu, then select Boot Arch Linux and press Enter.
  \end{itemize}

  You will be logged in on the first virtual console as the root user, and presented with a Zsh shell prompt.

  To switch to a different console—for example, to view this guide with Lynx alongside the installation—use the Alt+arrow shortcut. To edit configuration files, mcedit, nano and vim are available. See \texttt{pkglist.x86\_64.txt} for a list of the packages included in the installation medium.
\end{quote}
\end{question}

\end{document}

### 2025-01-18 Dustbound/Politics/2025_Shaanxi_Exam/paper.tex
feat: :sparkles: 正在使用 LaTeX 重排试题「2025 年陕西省高中学业水平选择性考试思想政治」

\documentclass{exam-zh}

\usepackage{xeCJK}
\usepackage{background}
\usepackage{needspace}
\usepackage{listing}

\examsetup{
  page = {
    foot-content = 「赴尘杯」思想政治试题第 ; 页（共 ; 页）
  }
}
\backgroundsetup{
  scale=20,
  color=black!10,
  opacity=1,
  angle=45,
  position=current page.center,
  contents={赴尘杯}
}

\newenvironment{kaiti-indented}{
  \parindent=2em % 设置首行缩进为两个汉字宽度
  \CJKfamily{zhkai} % 切换到楷体
}{
}

\title{2025 年陕西省高中学业水平选择性考试}
\subject[3.5em]{思想政治}

\begin{document}

\secret

\maketitle

本试卷共 16 页，67 题。全卷满分 150 分。考试用时 120 分钟。

\begin{notice}[][itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt]
\item 答卷前，考生务必将自己的姓名、准考证号填写在答题卡上。
\item 作答选择题时，选出每小题答案后，用 2B 铅笔在答题卡上对应题目选项的答案信息点涂黑，如需改动，用橡皮擦干净后，再选涂其他答案；作答非选择题时，用 0.5mm 黑色墨水签字笔在答题卡的对应题目位置作答，写在试题卷、草稿纸和答题卡上的非答题区域均无效。
\item 考试结束后，将本试卷和答题卡一并上交。
\end{notice}

\begin{flushleft}
{\bfseries 一、选择题：本题共 16 小题，每小题 3 分，共 48 分。在每小题给出的四个选项中，只有一个选项是正确的。请将正确的选项填涂在答题卡相应的位置上。)}
\end{flushleft}
\vspace{-1em}

\needspace{3\baselineskip}
\begin{question}
习近平总书记在 2025 年新年贺词中指出：党的二十届三中全会胜利召开，吹响进一步全面深化改革的号角。我们乘着改革开放的时代大潮阔步前行，中国式现代化必将在改革开放中开辟更加广阔的前景。由此可见

\circlednumber{1} 改革开放是决定当代中国命运的关键一招

\circlednumber{2} 党的二十届三中全会标志着中国特色社会主义进入了新阶段

\circlednumber{3} 全面深化改革有利于推进中国式现代化发展

\circlednumber{4} 中国共产党坚持始终走在时代前列

\begin{choices}
\item \circlednumber{1}\circlednumber{2}
\item \circlednumber{1}\circlednumber{3}
\item \circlednumber{2}\circlednumber{3}
\item \circlednumber{3}\circlednumber{4}
\end{choices}
\end{question}

\needspace{3\baselineskip}
\begin{question}
第二次世界大战后，资本主义有三大新变化：即新自由主义化、金融深化、全球经济虚拟化，这三大变化导致资本主义的不平等问题日益严重、经济出现停滞的趋势、泡沫经济和金融危机频发。由此可见

\circlednumber{1} 资本主义政府难以实现经济宏观调控

\circlednumber{2} 资本主义社会的基本矛盾是生产资料私有制和生产社会化的矛盾

\circlednumber{3} 资本主义的不平等问题可能随着生产力的不断发展而得到解决

\circlednumber{4} 周期性的资本主义经济危机是资本主义社会无法克服的障碍

\begin{choices}
\item \circlednumber{1}\circlednumber{2}
\item \circlednumber{1}\circlednumber{4}
\item \circlednumber{2}\circlednumber{3}
\item \circlednumber{2}\circlednumber{4}
\end{choices}
\end{question}

\needspace{3\baselineskip}
\begin{question}
某校思想政治学习小组收集了我国不同时期领导人的经济论述。

\begin{kaiti-indented}
江泽民说：实践的发展和认识的深化，要求我们明确提出，我国经济体制改革的目标是建立社会主义市场经济体制，以利于进一步解放和发展生产力。

胡锦涛说：提高开放水平，着力构建充满活力、富有效率、更加开放、有利于科学发展的体制机制，为发展中国特色社会主义提供强大动力和体制保障。

习近平说：坚持和完善我国社会主义基本经济制度和分配制度，毫不动摇巩固和发展公有制经济，毫不动摇鼓励、支持、引导非公有制经济发展，使市场在资源配置中起决定性作用，更好发挥政府作用。
\end{kaiti-indented}

对以上论述的分析合理的是

\circlednumber{1} 社会主义市场经济体制的建立和完善体现了党与时俱进的思想路线

\circlednumber{2} 社会主义市场经济体制要求毫不动摇巩固公有制经济主体地位

\circlednumber{3} 认识具有无限性，追求真理永无止境

\circlednumber{4} 改革是社会主义社会实现社会变革的决定力量

\begin{choices}
\item \circlednumber{1}\circlednumber{3}
\item \circlednumber{2}\circlednumber{3}
\item \circlednumber{2}\circlednumber{4}
\item \circlednumber{3}\circlednumber{4}
\end{choices}
\end{question}

\needspace{3\baselineskip}
\begin{question}
从党的十四届三中全会提出要建立社会保障制度，到党的十六大明确地把“社会保障体系比较健全”作为全面建设小康社会的目标之一，再到党的十八大把社会保障全民覆盖作为全面建成小康社会的重要目标，我国在推进社会保障制度建设的道路上行稳致远。以下说法合理的是

\circlednumber{1} 社会保障是政府承担主要责任的“安全网”

\circlednumber{2} 社会保障的运行方式是风险分摊和责任共担

\circlednumber{3} 只有参与劳动的社会成员才有权享受社会保险提供的保障

\circlednumber{4} 我国要最终建设覆盖全体人民的社会保障体系

\begin{choices}
\item \circlednumber{1}\circlednumber{2}
\item \circlednumber{1}\circlednumber{3}
\item \circlednumber{2}\circlednumber{3}
\item \circlednumber{2}\circlednumber{4}
\end{choices}
\end{question}

\needspace{3\baselineskip}
\begin{question}
自 2025 年 1 月 1 日起各大银行将执行新的存量房贷利率，且绝大多数借款人不需要提交额外申请或办理相关手续。以贷款额 100 万元、等额本息、30 年期限为例，在房贷利率从 3.9\% 下调至 3.3\% 后，每月利息支出可节省 300 多元。由此可见

\circlednumber{1} 中央人民政府通过调节财政政策刺激居民消费增长

\circlednumber{2} 房贷利率随市场波动调节体现了市场在资源配置中的决定性作用

\circlednumber{3} 中国人民银行积极促进金融业协调健康发展

\circlednumber{4} 我国政府坚持把人民幸福作为发展的最终目的

\begin{choices}
\item \circlednumber{1}\circlednumber{2}
\item \circlednumber{1}\circlednumber{3}
\item \circlednumber{2}\circlednumber{3}
\item \circlednumber{2}\circlednumber{4}
\end{choices}
\end{question}

\end{document}

### 2025-01-18 Dustbound/Politics/2025_Shaanxi_Exam/paper.tex
feat: :sparkles: 完稿 2025 年陕西省高中学业水平选择性考试思想政治 LaTeX 版

@@
 \usepackage{listing}
+\usepackage{setspace}
 
@@
 \newenvironment{kaiti-indented}{
-  \parindent=2em % 设置首行缩进为两个汉字宽度
-  \CJKfamily{zhkai} % 切换到楷体
+  \parindent=2em
+  \CJKfamily{zhkai}
+  \setstretch{1.4}
 }{
@@
 \begin{flushleft}
-{\bfseries 一、选择题：本题共 16 小题，每小题 3 分，共 48 分。在每小题给出的四个选项中，只有一个选项是正确的。请将正确的选项填涂在答题卡相应的位置上。)}
+  {\bfseries 一、选择题：本题共 16 小题，每小题 3 分，共 48 分。在每小题给出的四个选项中，只有一个选项是正确的。请将正确的选项填涂在答题卡相应的位置上。}
 \end{flushleft}
@@
 
+\needspace{3\baselineskip}
+\begin{question}
+  2024 年 12 月 26 日至 27 日，中共中央政治局召开民主生活会，会议上中央政治局的同志一致认为，以习近平同志为核心的党中央集中统一领导是做好一切工作的根本保证，确保中国式现代化航船乘风破浪、行稳致远，要坚持以习近平新时代中国特色社会主义思想为指导，坚持稳中求进工作总基调，扎实推动高质量发展，进一步全面深化改革，扩大高水平对外开放，保持社会和谐稳定。要求全体党员
+
+  \circlednumber{1} 把锤炼党性、提高思想觉悟作为根本课题
+
+  \circlednumber{2} 坚决维护以习近平同志为核心的党中央权威和集中统一领导
+
+  \circlednumber{3} 坚持人民立场，打造人民满意的服务型政府
+
+  \circlednumber{4} 始终走在时代前列，争做党和国家建设的先锋模范
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  第十四届全国人民代表大会代表中，少数民族代表总数的 14.85\%，全国 55 个少数民族都有本民族的代表；妇女代表占代表总数的 26.54\%，提高了 1.64 个百分点；一线工人、农民代表占代表总数的 16.69\%，提高了 0.99 个百分点；专业技术人员占代表总数的 21.30\%，提高了 0.73 个百分点。由此可见
+
+  \circlednumber{1} 全过程人民民主是最广泛的民主
+
+  \circlednumber{2} 人民代表大会能够把人民意愿通过法律程序上升为国家意志
+
+  \circlednumber{3} 我国的国体决定了人大代表的广泛性
+
+  \circlednumber{4} 人民代表大会制度保障各领域、各阶层人民充分享有民主权利
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{1}\circlednumber{4}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  2024 年 12 月 12 日，中国国民党革命委员会第十四届中央委员会第三次全体会议在北京闭幕。全国政协副主席、民革中央常务副主席何报翔提出：要切实把思想和行动统一到中共中央决策部署上来，更好担当起中国共产党的好参谋、好帮手、好同事的政治责任。由此可见
+
+  \circlednumber{1} 中国共产党领导各民主党派工作
+
+  \circlednumber{2} 中国共产党领导的多党合作和政治协商制度是符合中国国情的新型政党制度
+
+  \circlednumber{3} 人民政协始终坚持团结和民主为主题
+
+  \circlednumber{4} 政协委员通过向人民代表大会提交提案履行参政权
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  面对日益增长的环境问题，如何实现科学的、有质量的、可持续的发展成为新的时代课题。2005 年，时任浙江省委书记习近平创造性提出了“两山理论”：宁可不要金山银山也要绿水青山，因为绿水青山就是金山银山。党的十九大上，“两山理论”被写入党章。从中体现的哲学原理是
+
+  \circlednumber{1} 同一事物的两个对立面既相互矛盾又辩证统一
+
+  \circlednumber{2} 联系是客观的、普遍的，一切联系都以时间、地点和条件为转移
+
+  \circlednumber{3} 认识没有终点，科学没有顶峰
+
+  \circlednumber{4} 社会意识的变化发展可能影响社会存在的变化发展
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{4}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  观察三幅夏季奥运会会徽，可得出的认识有
+
+  \begin{multifigures}
+    \item[1952 年芬兰奥运会] \includegraphics[width=5cm]{helsinki.png}
+    \item[2008 年北京奥运会] \includegraphics[width=5cm]{beijing.png}
+    \item[2024 年巴黎奥运会] \includegraphics[width=5cm]{paris.png}
+  \end{multifigures}
+
+  \circlednumber{1} 文化是物质文明和精神文明繁荣的表现
+
+  \circlednumber{2} 继承和发扬中华优秀传统文化，需要实现中华优秀传统文化创新性发展
+
+  \circlednumber{3} 文化多样性是实现世界文化繁荣的必然要求
+
+  \circlednumber{4} 任何一种文化都是对当下时代精神的展现
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  2025 年 1 月 6 日，美国国会参众两院举行联席会议，依次递交第 60 届美国总统选举来自各州及华盛顿特区的选举人票投票结果，由两名参议员和两名众议员轮流唱票。结果显示，特朗普获得 312 张选举人票，超过赢得总统选举所需的 270 票，正式确认前总统、共和党总统候选人特朗普当选为美国总统。由此可见
+
+  \circlednumber{1} 美国国会参众两院拥有最高行政权力
+
+  \circlednumber{2} 美国总统由选民选举产生、对选民负责
+
+  \circlednumber{3} 美国的代议制政体维护了选民的政治权利
+
+  \circlednumber{4} 代议制是现代民主政体的共同特征
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  孙某 1999 年生，因先天性疾病导致其智力远低于同龄人。2018 年从特殊教育学校毕业后，在家附近的小超市当搬运工维持生活。由此可见
+
+  \circlednumber{1} 孙某有权通过劳动获得收入维持自身生活
+
+  \circlednumber{2} 国家设立专门教育机构保障特殊群体受教育权
+
+  \circlednumber{3} 孙某患有严重残疾，是无民事行为能力人
+
+  \circlednumber{4} 孙某接受慈善企业的爱心捐款，须经其监护人同意或追认
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  某学校在学生家庭情况调查中发现，本校学生小王因父母离异长期跟随父亲生活。小王父亲王某长期酗酒后对小王实施家庭暴力、长期侵占小王母亲支付的抚养费。该校有关负责人多次劝说无果后，决定报告公安机关并对王某提起诉讼。可能的结果有
+
+  \circlednumber{1} 公安机关发布对小王的人身安全保护令
+
+  \circlednumber{2} 人民法院判决王某失去小王的监护权
+
+  \circlednumber{3} 人民检察院对王某的家庭暴力行为继续追究刑事责任
+
+  \circlednumber{4} 民政部门解除小王与王某的父母子女关系
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{4}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  姜某和林某 2004 年生，从小青梅竹马。2024 年年末两人决定于 2025 年元旦当天办理结婚登记，且约定婚前个人的一切财产都属于夫妻共同财产。姜某父亲早年因公殉职，生前给妻子和姜某留下存款 20 万元。林某名下有一套位于某市繁华地段的商铺出租，每月可获得租金收入 2800 元。下列说法正确的是
+
+  \circlednumber{1} 根据约定，姜某分得的财产 10 万元和林某名下的商铺均属于夫妻共同财产
+
+  \circlednumber{2} 办理结婚登记前，两人的财产均为独立享有
+
+  \circlednumber{3} 姜某母亲独立承担抚养义务，占有 20 万元遗产的大部分继承权
+
+  \circlednumber{4} 若两人最终离婚，商铺依然属于共同财产
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{4}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  当一个主体的积极和消极两个方面同时出现在一个人的头脑中时，可能会也可能不会被体验为心理上的不愉快。这种不舒服的心理也被称为认知失调，会导致逃避、拖延，甚至故意尝试极端以解决这种心理。由此可见
+
+  \circlednumber{1} 逻辑思维遵循同一律的准则，事物的两方面最终趋于统一和确定
+
+  \circlednumber{2} 逻辑思维遵循矛盾律的准则，事物的两方面不能互相反对
+
+  \circlednumber{3} 人的思维来源于实践，正确的思维认识只能来源于实践
+
+  \circlednumber{4} 学习科学思维，必须坚持求真务实
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{3}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  化学上称只含有两种元素且元素之一为氧的化合物为氧化物。如果一种氧化物与碱反应只生成盐和水，则是酸性氧化物；如果一种氧化物与酸反应只生成盐和水，则是碱性氧化物；如果一种氧化物无论与酸或与碱反应均能生成盐和水，则是两性氧化物。酸性氧化物中大多数是非金属氧化物，非金属氧化物中大多数是酸性氧化物。下列推论正确的是
+
+  \circlednumber{1} 两性氧化物的断定方法属于联言判断
+
+  \circlednumber{2} 存在既非酸性氧化物也非金属氧化物的氧化物
+
+  \circlednumber{3} 酸性氧化物与碱性氧化物的概念外延属于矛盾关系
+
+  \circlednumber{4} 能与一种氧化物反应生成盐和水的物质必然是酸或碱
+
+  \begin{choices}
+  \item \circlednumber{1}\circlednumber{2}
+  \item \circlednumber{1}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{3}
+  \item \circlednumber{2}\circlednumber{4}
+  \end{choices}
+\end{question}
+
+\needspace{4\baselineskip}
+\begin{flushleft}
+  {\bfseries 二、非选择题：本题共 4 小题，共 52 分。}
+\end{flushleft}
+
+\needspace{3\baselineskip}
+\begin{question}
+  阅读材料，完成下列要求。
+
+  \begin{kaiti-indented}
+    1 月 9 日，陕西省十四届人大常委会第十四次会议在西安闭幕。会议表决通过了《黄帝陵保护条例》、《实施家庭教育促进法办法》和《陕西省法律援助条例》，表决通过了省人大常委会工作报告稿，根据表决结果决定任命李九红为陕西省副省长。
+
+    完成各项议程后，中共陕西省委书记、省人大常委会主任赵一德作了讲话。他强调，全省各级人大及其常委会要深入学习贯彻中央经济工作会议精神和习近平总书记近期一系列重要讲话重要指示精神，认真落实省委经济工作会议部署，主动适应进一步全面深化改革和经济社会发展需要，扎实做好立法、监督、决定、任免等各项工作，紧扣打造“四个机关”强化自身建设，为高质量完成“十四五”规划目标任务、奋力谱写中国式现代化建设的陕西新篇章贡献人大力量。
+  \end{kaiti-indented}
+
+  结合材料，运用《中国特色社会主义》《政治与法治》知识，分析陕西省人大常委会在坚持人民当家作主、党的领导、依法治国有机统一中发挥的作用。（11 分）
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  阅读材料，完成下列要求。
+
+  \begin{kaiti-indented}
+    近日，中共中央、国务院印发《关于深化养老服务改革发展的意见》，围绕加快建设符合我国国情的养老服务体系，优化基本养老服务供给，提出一揽子政策举措。
+
+    首次提出加快健全覆盖城乡的县乡村三级养老服务网络。根据《意见》部署，养老服务网络到2029年基本建成，到2035年更加健全。通过持续推进建设，把养老服务网织得更密更牢，稳稳兜住老年人的养老服务需求。
+
+    以推动三类养老服务贯通协调为改革重点，明确各类养老服务功能作用。加强各类养老服务在老年人需求场景的协调联动，让老年人在家庭、社区、机构都能享受方便可及的服务。
+
+    要大力发展银发经济，释放养老消费潜力。从消费趋势看，老年人与年轻人消费边界不断融合，消费观念、消费结构愈发重合，更加注重个性化和悦己消费，成为消费多元化发展的关键群体；从产业发展看，银发经济促使各产业为老年人创新、创造更多的服务产品，涉及老年人生活的方方面面，为老年人服务注入了新的动力。
+  \end{kaiti-indented}
+
+  （1）结合材料，运用《经济与社会》知识，阐述如何进一步建设养老服务体系。（9 分）
+
+  （2）结合材料，运用《哲学与文化》知识，对“银发产业经济效益弱，当前暂无必要大力发展”这一观点予以评价。（7 分）
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  阅读材料，完成下列要求。
+
+  \begin{kaiti-indented}
+    钱某是某县的一位知名女企业家。1997 年 5 月，钱某与孙某经亲戚介绍相识并决定结婚，孙某父母以价值 400 万元的一套独栋别墅作为彩礼赠与夫妻双方。婚礼时，孙某未达到规定的男性结婚年龄，后拖延到 1999 年 10 月才补办了结婚登记。1998 年 11 月，钱某的长子孙某甲出生。2004 年 1 月，次子孙某乙出生。2007 年 7 月，女儿孙某丙出生。钱某和孙某长期异地生活从事经商，2009 年 10 月，钱某因生意失败，欠下债务 300 万元并以此别墅作为抵押，约定分 15 年还清。2023 年，钱某病重，后经治疗无效逝世。清点钱某个人物品时，孙某发现钱某与情夫王某在外长期同居，还在 2012 年生育一女小王，并每月秘密向小王汇款抚养费 3000 元。债主要求支付 2023 年所欠分期款项时，孙某以不知情为由拒绝支付。2025 年 1 月，孙某因车祸不幸逝世，获得肇事车主 85 万元赔偿。
+  \end{kaiti-indented}
+
+  根据材料，运用《法律与生活》知识，对本题中所有继承权、债权、抚养权进行合理配置。（15 分）
+\end{question}
+
+\needspace{3\baselineskip}
+\begin{question}
+  阅读材料，完成下列要求。
+
+  \begin{kaiti-indented}
+    日本出租车行业破产数量正在急剧增加。日本帝国数据库网日前发布的数据显示，2024 年日本国内发生的出租车公司倒闭清算 35 件，停业、解散 47 件，共计 82 家出租车公司选择退出市场，与 2023 年 全年 63 件相比增加 19 件、增长了 30.2\%，超过了 2019 年的 73 件，创历史新高。报告称，在 2024 年出租车行业的 35 起破产中，至少四成以上的主要原因是司机等人手不足。出租车司机短缺情况日益严重，以及因人手不足而带来的出租车车辆剩余，进而导致车辆运转率下降，给各家出租车公司运营造成严重影响。日本国土交通省数据显示，截至 2023 年 3 月底，日本全国在出租车公司工作的司机约为 22 万人，与疫情前 2019 年 3 月相比减少了约两成。相比之下，法人出租车保有车辆的减少幅度不足10\%，司机减少速度远超车辆数量的下降。供需错配进一步加重了行业困境。此外，出租车主要燃料价格的持续高涨也对出租车企业造成了沉重负担。日本液化石油气价格飞涨，能源成本增加，经营压力显著加剧，也是导致出租车运营商放弃业务数量增加的一个因素。
+  \end{kaiti-indented}
+
+  根据材料，运用《逻辑与思维》知识，运用科学思维说明中国出租车行业可以吸取的行
+  业经验和做法，并说明所使用的科学思维方法。（10 分）
+\end{question}
+
 \end{document}

### 2025-01-19 Dustbound/Politics/2025_Shaanxi_Exam/paper.tex
fix: :lipstick: 修复了 Question 10 图片超界的问题

@@
 
-\secret
+\begin{flushleft}
+  {\bfseries 机密 \star 启用前}
+\end{flushleft}
+\vspace{-1em}
 
@@
 
-本试卷共 16 页，67 题。全卷满分 150 分。考试用时 120 分钟。
+本试卷共 6 页，20 题。全卷满分 100 分。考试时间 75 分钟。
 
@@
   \begin{multifigures}
-    \item[1952 年芬兰奥运会] \includegraphics[width=5cm]{helsinki.png}
-    \item[2008 年北京奥运会] \includegraphics[width=5cm]{beijing.png}
-    \item[2024 年巴黎奥运会] \includegraphics[width=5cm]{paris.png}
+    \item[\CJKfamily{zhkai} 1952 年芬兰奥运会] \includegraphics[width=4cm]{helsinki.png}
+    \item[\CJKfamily{zhkai} 2008 年北京奥运会] \includegraphics[width=4cm]{beijing.png}
+    \item[\CJKfamily{zhkai} 2024 年巴黎奥运会] \includegraphics[width=4cm]{paris.png}
   \end{multifigures}
@@
 \end{question}
+\vspace{-0.5em}
 

### 2025-01-19 Dustbound/English/Dustbound_English_I/paper.tex
fix: :pencil2: 修复了一处括号全半角不匹配问题
feat: 添加 B 篇阅读

@@
 
-{\bfseries 第一节（共 15 小题；每小题 2.5 分，满分 37.5 分)}
+{\bfseries 第一节（共 15 小题；每小题 2.5 分，满分 37.5 分）}
 \end{flushleft}
@@
 
+\needspace{4\baselineskip}
+{\centering \bfseries B \par}
+
+{\centering \bfseries Passerine / Dream SMP Fanwork - Chapter 1 \par}
+
+“You’re a bastard,” Techno said playfully, even as the voices screamed, run, run, run.
+He took Philza’s offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword’s edge was.
+As Philza patiently moved Techno through all the things he’d done wrong (small things like foot placement and his hilt grip being an inch off), Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique.
+But then again, Techno’s technique wasn’t particularly polished; it took only one brutal swing to fell most people.
+Something told him that Philza would be harder to kill than that.
+
+They conquered nations, he and his golden-haired friend.
+They were bathed in glory, twin gods shining in the middle of a bloody fields.
+But as their empire grew, so did their enemies.
+They came in droves, day after day, and before long Techno had forgotten what peace tasted like.
+The days were long and the nights were longer; every flicker of movement was a spy in the shadows, every ally was a potential traitor, every word was a declaration of war.
+Their home had become a target for a thousand armies.
+
+Through it all, his one constant was Philza—until he wasn’t.
+Technoblade simply looked up one day from a map detailing enemy lines and realized he’d been talking to empty air.
+He had no idea how long he’d been alone, sitting in a dusty library with stale tea untouched in the corner.
+He had no idea if Philza ever said he was leaving, or if he simply went as he arrived suddenly, swiftly, like a snowstorm.
+
+Afterwards, there was hardly any point in maintaining the empire.
+The voices were getting bored, anyway.
+They wanted more.
+A fresh fight, more stories.
+So Techno took his sword and his shield, and abandoned ship.
+He’d done it a million times before, but the thought of a chess board lying unused in a crumbling castle made him feeling something close to regret.
+
+Technoblade wandered the world, trying to appease the voices.
+Neither of them were ever satisfied.
+No matter how much chaos he dealt, there was always more work to be done.
+So he worked.
+He had no idea for how long.
+All he remembered from that bloody time was a sense of unfulfillment, like a story had been left unfinished halfway through.
+Years.
+Decades.
+Maybe more.
+It hardly mattered.
+
+In the end, he knew, it would all be the same.
+The world would end, and he would remain—always fighting, always alone.
+He’d seen it in his dreams, in the visions that plagued him.
+The world would end, and he would remain.
+
+\needspace{4\baselineskip}
+\begin{question}
+What is the relationship between Technoblade and Philza in the story?
+\begin{choices}
+  \item They are twin gods who have conquered nations and are bathed in glory.
+  \item They are friends who have fought side by side and have grown apart over time.
+  \item They are enemies who have fought each other for eons and have never been able to kill each other.
+  \item They are allies who have been betrayed by their enemies and have been forced to abandon their empire.
+\end{choices}
+\end{question}
+
+\needspace{4\baselineskip}
+\begin{question}
+What is the main reason for Technoblade to abandon his empire and wander the world?
+\begin{choices}
+  \item He was bored with the empire and wanted to find new challenges.
+  \item He was betrayed by his allies and was forced to leave the empire.
+  \item He was haunted by the voices in his head and was unable to find peace.
+  \item He was tired of fighting and wanted
+\end{choices}
+\end{question}
+
+\needspace{4\baselineskip}
+\begin{question}
+What is the author's attitude towards the relationship between Technoblade and Philza?
+\begin{choices}
+  \item Neutral.
+  \item Sympathetic.
+  \item Critical.
+  \item Humorous.
+\end{choices}
+\end{question}
+
+\needspace{4\baselineskip}
+\begin{question}
+What is the main theme of the story?
+\begin{choices}
+  \item The importance of friendship and loyalty.
+  \item The inevitability of conflict and betrayal.
+  \item The futility of power and glory.
+  \item The loneliness of eternal existence.
+\end{choices}
+\end{question}
+
 \end{document}

### 2025-01-19 Dustbound/English/Dustbound_English_I/paper.tex
fix: fill some contents
fix: :bug: 修复了中文引号在 LaTeX 中渲染的问题

@@
 The only way to prevent anyone with physical access from disabling Secure Boot is to protect the firmware settings with a password.
-Most UEFI firmwares provide such a feature, usually listed under the "Security" section in the firmware settings.
+Most UEFI firmwares provide such a feature, usually listed under the ``Security'' section in the firmware settings.
 
@@
 \item Recent iterations of Xiaomi laptops give users access to the configuration of Secure Boot within the firmware only if the administrator password remains active after setting up.
-Users can possibly set the password in the "Security" section in the firmware settings.
+Users can possibly set the password in the ``Security'' section in the firmware settings.
 
@@
 If you do this, and someone e.g.
-steals your PC, this person can delete the personal Platform Key in the UEFI Secure Boot firmware again, turn on "Setup Mode" on your PC again and replace your Secure Boot Keys (PK, KEK, db, dbx) with their own Platform Key, thereby defeating the whole purpose of UEFI Secure Boot.
+steals your PC, this person can delete the personal Platform Key in the UEFI Secure Boot firmware again, turn on ``Setup Mode'' on your PC again and replace your Secure Boot Keys (PK, KEK, db, dbx) with their own Platform Key, thereby defeating the whole purpose of UEFI Secure Boot.
 Only you should be able to replace the Platform Key, so only you should have access to the \texttt{noPK.auth} file.
@@
 
-“You’re a bastard,” Techno said playfully, even as the voices screamed, run, run, run.
-He took Philza’s offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword’s edge was.
-As Philza patiently moved Techno through all the things he’d done wrong (small things like foot placement and his hilt grip being an inch off), Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique.
-But then again, Techno’s technique wasn’t particularly polished; it took only one brutal swing to fell most people.
+``You're a bastard,'' Techno said playfully, even as the voices screamed, ``Run, run, run.'' He took Philza's offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword's edge was.
+As Philza patiently moved Techno through all the things he'd done wrong—small things like foot placement and his hilt grip being an inch off—Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique.
+But then again, Techno's technique wasn't particularly polished; it took only one brutal swing to fell most people.
 Something told him that Philza would be harder to kill than that.
@@
 They conquered nations, he and his golden-haired friend.
-They were bathed in glory, twin gods shining in the middle of a bloody fields.
+They were bathed in glory, twin gods shining in the middle of bloody fields.
 But as their empire grew, so did their enemies.
@@
 
-Through it all, his one constant was Philza—until he wasn’t.
-Technoblade simply looked up one day from a map detailing enemy lines and realized he’d been talking to empty air.
-He had no idea how long he’d been alone, sitting in a dusty library with stale tea untouched in the corner.
-He had no idea if Philza ever said he was leaving, or if he simply went as he arrived suddenly, swiftly, like a snowstorm.
+Through it all, his one constant was Philza—until he wasn't.
+Technoblade simply looked up one day from a map detailing enemy lines and realized he'd been talking to empty air.
+He had no idea how long he'd been alone, sitting in a dusty library with stale tea untouched in the corner.
+He had no idea if Philza ever said he was leaving, or if he simply went as he arrived—suddenly, swiftly, like a snowstorm.
 
@@
 So Techno took his sword and his shield, and abandoned ship.
-He’d done it a million times before, but the thought of a chess board lying unused in a crumbling castle made him feeling something close to regret.
+He'd done it a million times before, but the thought of a chessboard lying unused in a crumbling castle made him feel something close to regret.
 
 Technoblade wandered the world, trying to appease the voices.
-Neither of them were ever satisfied.
+Neither of them was ever satisfied.
 No matter how much chaos he dealt, there was always more work to be done.
@@
 The world would end, and he would remain—always fighting, always alone.
-He’d seen it in his dreams, in the visions that plagued him.
+He'd seen it in his dreams, in the visions that plagued him.
 The world would end, and he would remain.
@@
   \item He was haunted by the voices in his head and was unable to find peace.
-  \item He was tired of fighting and wanted
+  \item He was tired of fighting and wanted to find a way to end the world.
 \end{choices}

### 2025-01-19 Dustbound/English/Dustbound_English_I/paper.tex
feat: :art: 加入七选五材料，并进行了破折号和引号的修改
Co-authored-by: hello8693 <1320998105@qq.com>
Co-authored-by: Aris <test_bl@outlook.com>

@@
 
-``You're a bastard,'' Techno said playfully, even as the voices screamed, ``Run, run, run.'' He took Philza's offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword's edge was.
+``You're a bastard,'' Techno said playfully, even as the voices screamed, Run, run, run.'' He took Philza's offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword's edge was.
 As Philza patiently moved Techno through all the things he'd done wrong—small things like foot placement and his hilt grip being an inch off—Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique.
@@
 
+\needspace{4\baselineskip}
+\begin{flushleft}
+  {\bfseries 第二节（共 5 小题；每小题 2.5 分，满分 12.5 分）}
+\end{flushleft}
+
+阅读下面短文，从短文后的选项中选出可以填入空白处的最佳选项。选项中有两项为多余选项。
+
+{\centering \bfseries Why fairy tales are really scary tales \par}
+
+\begin{center}
+  \texttt{Some people think that fairy tales are just stories to amuse children, but their universal and enduring appeal may be due to more serious reasons}
+\end{center}
+
+People of every culture tell each other fairy tales, but the same story often takes a variety of forms in different parts of the world.
+In the story of \textit{Little Red Riding Hood} that European children are familiar with, a young girl on the way to see her grandmother meets a wolf and tells him where she is going.
+The wolf runs on ahead and disposes of the grandmother, then gets into bed dressed in the grandmother's clothes to wait for \textit{Little Red Riding Hood}.
+You may think you know the story—but which version?
+In some versions, the wolf swallows up the grandmother, while in others it locks her in a cupboard.
+In some stories Red Riding Hood gets the better of the wolf on her own, while in others a hunter or a woodcutter hears her cries and comes to her rescue.
+
+The universal appeal of these tales is frequently attributed to the idea that they contain cautionary messages: in the case of \textit{Little Red Riding Hood}, to listen to your mother, and avoid talking to strangers.
+``It might be what we find interesting about this story is that it's got this survival relevant information in it,'' says anthropologist Jamie Tehrani at Durham University in the UK.
+But his research suggests otherwise.
+``We have this huge gap in our knowledge about the history and prehistory of storytelling, despite the fact that we know this genre is an incredibly ancient one,'' he says.
+That hasn't stopped anthropologists, folklorists and other academics devising theories to explain the importance of fairy tales in human society.
+Now Tehrani has found a way to test these ideas, borrowing a technique from evolutionary biologists.
+
+To work out the evolutionary history, development and relationships among groups of organisms, biologists compare the characteristics of living species in a process called ``phylogenetic analysis''.
+Tehrani has used the same approach to compare related versions of fairy tales to discover how they have evolved and which elements have survived longest.
+
+Tehrani's analysis focused on \textit{Little Red Riding Hood} in its many forms, which include another Western fairy tale known as The Wolf and the Kids.
+Checking for variants of these two tales and similar stories from Africa, East Asia and other regions, he ended up with 58 stories recorded from oral traditions.
+Once his phylogenetic analysis had established that they were indeed related, he used the same methods to explore how they have developed and altered over time.
+
+First he tested some assumptions about which aspects of the story alter least as it evolves, indicating their importance.
+Folklorists believe that what happens in a story is more central to the story than the characters in it—that visiting a relative, only to be met by a scary animal in disguise, is more fundamental than whether the visitor is a little girl or three siblings, or the animal is a tiger instead of a wolf.
+
+However, Tehrani found no significant difference in the rate of evolution of incidents compared with that of characters.
+``Certain episodes are very stable because they are crucial to the story, but there are lots of other details that can evolve quite freely,'' he says.
+Neither did his analysis support the theory that the central section of a story is the most conserved part.
+He found no significant difference in the flexibility of events there compared with the beginning or the end.
+
+But the really big surprise came when he looked at the cautionary elements of the story.
+``Studies on hunter-gatherer folk tales suggest that these narratives include really important information about the environment and the possible dangers that may be faced there—stuff that's relevant to survival,'' he says.
+Yet in his analysis such elements were just as flexible as seemingly trivial details.
+What, then, is important enough to be reproduced from generation to generation?
+
+The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all.
+Why are these details retained by generations of storytellers, when other features are not?
+Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller.
+\fillin[A]'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.
+
+Jack Zipes at the University of Minnesota, Minneapolis, is unconvinced by Tehrani's views on fairy tales.
+``Even if they're gruesome, they won't stick unless they matter,'' he says.
+He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant.
+But Tehrani points out that although this is often the case in Western versions, it is not always true elsewhere.
+In Chinese and Japanese versions, often known as \textit{The Tiger Grandmother}, the villain is a woman, and in both Iran and Nigeria, the victim is a boy.
+
+Mathias Clasen at Aarhus University in Denmark isn't surprised by Tehrani's findings.
+``Habits and morals change, but the things that scare us, and the fact that we seek out entertainment that's designed to scare us—those are constant,'' he says.
+Clasen believes that scary stories teach us what it feels like to be afraid without having to experience real danger, and so build up resistance to negative emotions.
+
+\begin{choices}
+\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller.
+\end{choices}
+
 \end{document}

### 2025-01-20 Dustbound/English/Dustbound_English_I/paper.tex
feat: :sparkles: 英语 I 七选五题目完成~

@@
   page = {
-    foot-content = 「赴尘杯」英语试题第 ; 页（共 ; 页）
+    foot-content = 「赴尘杯」英语试题第 ; 页（共 ;页）
   }
@@
 ``It might be what we find interesting about this story is that it's got this survival relevant information in it,'' says anthropologist Jamie Tehrani at Durham University in the UK.
-But his research suggests otherwise.
+\fillin[A].
 ``We have this huge gap in our knowledge about the history and prehistory of storytelling, despite the fact that we know this genre is an incredibly ancient one,'' he says.
@@
 First he tested some assumptions about which aspects of the story alter least as it evolves, indicating their importance.
-Folklorists believe that what happens in a story is more central to the story than the characters in it—that visiting a relative, only to be met by a scary animal in disguise, is more fundamental than whether the visitor is a little girl or three siblings, or the animal is a tiger instead of a wolf.
+\fillin[D]—that visiting a relative, only to be met by a scary animal in disguise, is more fundamental than whether the visitor is a little girl or three siblings, or the animal is a tiger instead of a wolf.
 
@@
 The answer, it would appear, is fear—blood-thirsty and gruesome aspects of the story, such as the eating of the grandmother by the wolf turned out to be the best preserved of all.
-Why are these details retained by generations of storytellers, when other features are not?
+\fillin[B]?
 Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller.
-\fillin[A]'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.
+\fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.
 
@@
 ``Even if they're gruesome, they won't stick unless they matter,'' he says.
-He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant.
+\fillin[F].
 But Tehrani points out that although this is often the case in Western versions, it is not always true elsewhere.
@@
 \begin{choices}
-\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller.
+\item But his research suggests otherwise
+\item Why are these details retained by generations of storytellers, when other features are not
+\item It also needs to be interesting when it's told by someone who's not necessarily a great storyteller
+\item Folklorists believe that what happens in a story is more central to the story than the characters in it
+\item According to folklorists, the impression left by a story’s characters tends to be stronger than that of the events unfolding within it
+\item He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant
+\item He holds the point that fairy tales continue to be passed down through generations because they frequently depict women as storytellers
 \end{choices}

### 2025-01-20 Dustbound/English/Dustbound_English_I/paper.tex
feat: :construction: 加入语法填空

@@
     foot-content = 「赴尘杯」英语试题第 ; 页（共 ;页）
+  },
+  fillin = {
+    show-answer = false,
+    no-answer-type = counter,
+    no-answer-counter-index = 36
   }
@@
 \fillin[B]?
-Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller.
-\fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.
+Tehrani has an idea: ``In an oral context, a story won't survive because of one great teller.\linebreak \fillin[C].'' Maybe being swallowed whole by a wolf, then cut out of its stomach alive is so gripping that it helps the story remain popular, no matter how badly it's told.
 
@@
 \item Folklorists believe that what happens in a story is more central to the story than the characters in it
-\item According to folklorists, the impression left by a story’s characters tends to be stronger than that of the events unfolding within it
+\item According to folklorists, the impression left by a story's characters tends to be stronger than that of the events unfolding within it
 \item He believes the perennial theme of women as victims in stories like \textit{Little Red Riding Hood} explains why they continue to feel relevant
@@
 
+\begin{flushleft}
+  {\bfseries 第三部分 \hspace{0.5em} 语言运用（共两节，满分 30 分）}
+
+  {\bfseries 第一节（共 15 小题；每小题 1 分，满分 15 分）}
+\end{flushleft}
+
+阅读下面短文，从每题所给的 A、B、C 和 D 四个选项中选出最佳答案。
+
+\begin{flushleft}
+  {\bfseries 第二节（共 10 小题；每小题 1.5 分，满分 15 分）}
+\end{flushleft}
+
+阅读下面短文，在空白处填入 1 个适当的单词或括号内单词的正确形式。
+
+As a dog lover, our canine companions always fill me with joy.
+Whether pedigree or mongrel, tame or stray, whenever I see one, I smile.
+After all, their loyalty is \fillin[indisputable] (dispute), their companionship is always welcome—they fetch for us, guard for us and even work for us when required.
+Good old Fido has always been close to \fillin[mine 或 my] (me), and many other's hearts.
+
+Well, not content \fillin[with] just \fillin[warming] (warm) the cockles of your heart, it seems that our four-legged-friends actually lower the risk of cardiovascular disease, according to a 2017 scientific study, which looked at 3.4 million Swedes from 2001 to 2012.
+
+The study concluded that this lower risk, which was particularly evident in owners of hunting breeds, may not just be due to the \fillin[increasing] (increase) physical activity that goes hand-in-hand with owning a dog, but could also be down to dogs increasing the owner's social contact, or \fillin[by] changing the owner's bacterial microbiome, which is the collection of microscopic species that live in \fillin[their] gut.
+Dogs change the \fillin[dirt] (dirty) in home environments and therefore expose people to bacteria that they would otherwise not encounter.
+
+These effects were particularly marked in those who lived on their lonesome.
+According to Mwenya Mubanga of Uppsala University and lead author of the study, ``single dog owners had a 33\% reduction in risk of death and an 11\% reduction in risk of cardiac arrest compared to single non-owners.''
+
+However, before your heart skips a beat, Tove Fall, senior author of the study, also adds that there may be limitations.
+It's possible that the differences between owners and non-owners, which already existed \fillin[before] the dog was bought, could have influenced the results—or that people who are generally more active also tend to get a dog anyway.
+
+It seems that the results are not as clear cut as they initially appear to be, but as far as I'm concerned, that's ok.
+I love dogs for \fillin[whether] they make me feel and, cardiovascular benefits or not, they'll always be top dog to me—cross my heart.
+
 \end{document}
